An OpenCL Implementation of Wait-Free Sets

### 2015-07-02 Docs/paper.tex
doc changed

>>>>

\section{The Algorithm}
The algorithm consists of a modification of the wait-free linked list to support replacing a node.

A {\it packed} reference consists of an unmarked reference, a {\it mark} bit to indicate if the node is marked and an {\it retain} bit to indicate that unmarked reference could not be changed. It also has a {\it free} bit to indicate that whether the node is occupied or free. These three bits are arranged as $Bits = [fBit,rBit,mBit]$.

We also have the following methods

\begin{enumerate}
    \item $[ref, bits] = unpackRef(pref)$.
\end{enumerate}

\begin{algorithm}
  \caption{snips next node if it is marked and could be snipped}
  \label{alg:snip}

  \begin{algorithmic}[1]
    \Require
        \Statex startRef:Reference to the starting node.
    \Ensure
       \Statex next node will be snipped.
    \Statex   
    \Function{snip}{startRef}
      \State pPRef = startRef:next;
      \State [nRef,pBits] = unpackRef(startRef:next);
      \If{(pBits = [0,0,0])}
        \State [nnRef,nBits] = unpackRef(pRef:next):
        \If{(nBits = [0,x,1])}
          \State status = CAS(startRef:next,pPRef,[nnRef,pBits]);
          \State
          \Return status;
        \Else
          \State
          \Return false;
        \EndIf
      \Else
        \State
        \Return false;
      \EndIf
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}
  \caption{Replaces next node with a new node}
  \label{alg:replace}

  \begin{algorithmic}[1]
    \Require
        \Statex startRef:Reference to the starting node.
    \Ensure
       \Statex next node will be replaced by new node.
    \Statex   
    \Function{replace}{startRef, newRef}
      \State pPRef = startRef:next;    
      \State [nRef,pBits] = unpackRef(startRef:next);
      \If{([pBits] = [0,0,0])}
        \State nPRef = nRef:next;    
        \State [nnRef,nBits] = unpackRef(nRef:next);
        \If{(nBits = [0,x,0])}
          \State status = CAS(nRef:next,nPRef,[nnRef,[0,1,0]]);
          \If{(status = false)}
            \State
            \Return false;
          \EndIf  
        \Else
          \State
          \Return false;
        \EndIf
        \State newRef:next = [nnRef,[0,0,0]];
        \State status = CAS(startRef:next,pPRef,[newRef,pBits]);
        \If{(status = false)}
          \State
          \Return false;
        \EndIf
      \Else
        \State
        \Return false;
      \EndIf
      \State
      \Return true;
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}
  \caption{cleans all the nodes that are logically deleted and could be physically deleted}
  \label{alg:clean}
  \begin{algorithmic}[1]
    \Require
        \Statex startRef:Reference to the starting node.
    \Ensure
       \Statex cleans all the logically deleted nodes.
    \Statex   
    \Function{clean}{startRef, nextRef\&}
      \State pRef  = startRef;
      \While{(done = 0)}
        \State nPRef = pRef:next;
        \State [nRef,prBit,pmBit] = unpackRef(nPRef);
        \If({prBit = 0})
          \State status = snip(pRef);
        \Else
          \State   
        \EndIf
      \EndWhile
    \EndFunction
  \end{algorithmic}
\end{algorithm}
